---
title: "Nucl_Data analysis"
output: html_document
---

```{r,include=FALSE}
library(tidyverse)
library(ggplot2)
library(grid)
library(gridExtra)
```

```{r}
multMerge = function(mypath){
  filenames = list.files(path = mypath, full.names = TRUE)
  datalist = lapply(filenames, 
                    function(x){read.csv(file = x,
                                         header = TRUE,
                                         stringsAsFactors = FALSE)})
  Reduce(function(x,y) {merge(x, y, all = TRUE)}, datalist)
}

nucldata <- multMerge('data')

nucldata_cleaned_full <- nucldata[, which(colMeans(!is.na(nucldata)) > 0.90)]

write.csv(nucldata_cleaned_full,'nucldata_cleaned_full.csv',row.names = F)
```

Let see on our data on boxplots:

```{r, warning=FALSE}
qplot(as.factor(species_name), Angle_between_COM_and_Calpha_of_hel_7, data = nucldata_cleaned_full, 
      geom=c("boxplot"), fill=as.factor(preparation), xlab='Prepared', ylab='Angle between COM and Calpha of helix 7') + 
  labs(fill = "Is it prepared")
```



Because our data is not so clean and definitely not-parametric, let use non parametric tests to find difference. Wilcox test with Bonferroni adjust to check differences in data before and after preparation:
```{r}
res_prep <- nucldata_cleaned_full[,-c(1,2,3,4)] %>% 
  select_if(is.numeric) %>%
  map_df(~ broom::tidy(wilcox.test(. ~nucldata_cleaned_full$preparation)), .id = 'var')
res_prep$p.value = p.adjust(res_prep$p.value, method = 'bonferroni')
```

And Kruskal test with Bonferroni adjust to check differences between species, because our data have more than two gradations of factor:
```{r}
res_spec <- nucldata_cleaned_full[,-c(1,2,3,4)] %>% 
  select_if(is.numeric) %>%
  map_df(~ broom::tidy(kruskal.test(. ~ as.factor(nucldata_cleaned_full$species_name))), .id = 'var')
res_spec$p.value = p.adjust(res_spec$p.value, method = 'bonferroni')
```

Subset of our data with statistically significant data.
```{r}
res_prep_sig <- res_prep %>% filter(res_prep$p.value < 0.05)
res_spec_sig <- res_spec %>% filter(res_spec$p.value < 0.05)
```

Top 25 most significant differences in preparation
```{r}
myTable <- tableGrob(
  as.data.frame(res_prep_sig)[0:25,], 
  rows = NULL, 
  theme = ttheme_default(8, padding = unit(c(0,2),"mm"))
)

grid.newpage()
grid.draw(myTable)
```


Top 25 most significant differences in species
```{r}
myTable <- tableGrob(
  as.data.frame(res_spec_sig[order(res_spec_sig$p.value),])[0:25,], 
  rows = NULL, 
  theme = ttheme_default(8, padding = unit(c(0,2),"mm"))
)

grid.newpage()
grid.draw(myTable)
```


